On the performance of the MAC model

### 2018-11-02 2018_nips_vigil/appendix.tex
Comparison on CoGenT, external values

Along with CLEVR, the authors~\cite{johnson2017clevr} introduced  CLEVR-CoGenT (Compositional Generalization Test, CoGenT in short), with a goal of testing how well the models can learn and generalize compositional concepts.
This dataset is synthesized in the same way as CLEVR, but contains two conditions.
As shown in \tableref{tab:cogent_conditions}, in Condition A all cubes are gray, blue, brown, or yellow, whereas all cylinders are red, green, purple, or cyan; in Condition B cubes and cylinders swap color palettes.
Both conditions contain spheres of all colors.
CoGenT thus indicates how a model answers CLEVR questions: by memorizing combinations of traits or by learning disentangled or general representations.
The CoGenT dataset contains:
\begin{itemize}
\item	A training set of 70,000 images and 699,960 questions in Condition A,
\item	A validation set of 15,000 images and 150,000 questions in Condition A,
\item	A validation set of 15,000 images and 149,991 questions in Condition B,
\item	A test set of 15,000 images and 149,980 questions in Condition B,
\item	A test set of 15,000 images and 149,992 questions in Condition B,
\item	Answers, scene graphs and functional programs for all training and validation images and questions.
\end{itemize}

@@

\begin{table}[!h]
	\caption{Generalization capabilities of selected state-of-the-art models}
	\centering
	\begin{tabular}{cCcCcCc}
		\toprule
		Model & \multicolumn{2}{c}{Training} &    \multicolumn{2}{c}{Fine-tuning} &   \multicolumn{2}{c}{Test} \\		
		\cmidrule{2-3} \cmidrule{4-5}\cmidrule{6-7}
		(source)& CoGenT-A set & Acc [\%]  & CoGenT-B set & Acc [\%]  & CoGenT set~ & Acc [\%] \\

\midrule				
& \multirow{5}{*}{Training Full?}   & \multirow{5}{*}{N/A}  & \multirow{2}{*}{--} & \multirow{2}{*}{--}  &   A Test?    &   96.6  \\
\cmidrule{6-7} 
PG+EE &   &    &   &    & B Test Full?    &   73.7  \\
\cmidrule{4-5}\cmidrule{6-7}
(\cite{johnson2017inferring}) &  &    & \multirow{2}{*}{B Train 30k?}  & \multirow{2}{*}{N/A}     & A Test?    &   76.1 \\
\cmidrule{6-7} 
&   &    &   &    & B Test Full?    &   92.7  \\

\midrule				
& \multirow{5}{*}{xxx}   & \multirow{5}{*}{N/A}  & \multirow{2}{*}{--} & \multirow{2}{*}{--}  &   AAA    &     \\
\cmidrule{6-7} 
MAC &   &    &   &    & BBB    &     \\
\cmidrule{4-5}\cmidrule{6-7}
(\cite{hudson2018compositional}) &  &    & \multirow{2}{*}{CoGenT-B}  & \multirow{2}{*}{N/A}     & CoGenT-A    &   \\
\cmidrule{6-7} 
&   &    &   &    & CoGenT-B    &    \\

\midrule				
& \multirow{5}{*}{A Train 670k}   & \multirow{5}{*}{xx}  & \multirow{2}{*}{--} & \multirow{2}{*}{--}  &   A Valid 30k    &     \\
\cmidrule{6-7} 
MAC &   &    &   &    & CoGenT-B    &     \\
\cmidrule{4-5}\cmidrule{6-7}
(ours) &  &    & \multirow{2}{*}{CoGenT-B 30k}  & \multirow{2}{*}{N/A}     & CoGenT-A    &   \\
\cmidrule{6-7} 
&   &    &   &    & CoGenT-B    &    \\

\midrule				
& \multirow{5}{*}{CoGenT-A}   & \multirow{5}{*}{N/A}  & \multirow{2}{*}{--} & \multirow{2}{*}{--}  &   CoGenT-A    &     \\
\cmidrule{6-7} 
S-MAC &   &    &   &    & CoGenT-B    &     \\
\cmidrule{4-5}\cmidrule{6-7}
(ours) &  &    & \multirow{2}{*}{CoGenT-B 30k}  & \multirow{2}{*}{N/A}     & CoGenT-A    &   \\
\cmidrule{6-7} 
&   &    &   &    & CoGenT-B    &    \\

@@

@@

>>>>

Along with CLEVR, the authors~\cite{johnson2017clevr} introduced  CLEVR-CoGenT (Compositional Generalization Test, CoGenT in short), with a goal of testing how well the models can learn and generalize compositional concepts.
This dataset is synthesized in the same way as CLEVR, but contains two conditions.
As shown in \tableref{tab:cogent_conditions}, in Condition A all cubes are gray, blue, brown, or yellow, whereas all cylinders are red, green, purple, or cyan; in Condition B cubes and cylinders swap color palettes.
Both conditions contain spheres of all colors.
CoGenT thus indicates how a model answers CLEVR questions: by memorizing combinations of traits or by learning disentangled or general representations.
The CoGenT dataset contains:
\begin{itemize}
\item	Training set of 70,000 images and 699,960 questions in Condition A,
\item	Validation set of 15,000 images and 149,991 questions in Condition A,
\item	Test set of 15,000 images and 149,980 questions in Condition A (without answers),
\item	Validation set of 15,000 images and 150,000 questions in Condition B,
\item	Test set of 15,000 images and 149,992 questions in Condition B (without answers),
\item	Answers, scene graphs and functional programs for all training and validation images and questions.
\end{itemize}

@@

\begin{table}[!h]
	\caption{Generalization capabilities of selected state-of-the-art models}
	\centering
	\begin{tabular}{cCcCcCc}
		\toprule
		Model & \multicolumn{2}{c}{Training} &    \multicolumn{2}{c}{Fine-tuning} &   \multicolumn{2}{c}{Test} \\		
		\cmidrule{2-3} \cmidrule{4-5}\cmidrule{6-7}
		(source)& CoGenT set & Acc [\%]  & CoGenT set & Acc [\%]  & CoGenT set~ & Acc [\%] \\

\midrule				
& \multirow{5}{*}{A Train Full?}   & \multirow{5}{*}{N/A}  & \multirow{2}{*}{--} & \multirow{2}{*}{--}  &   A Test Full    &   96.6  \\
\cmidrule{6-7} 
PG+EE &   &    &   &    & B Test Full?    &   73.7  \\
\cmidrule{4-5}\cmidrule{6-7}
(\cite{johnson2017inferring}) &  &    & \multirow{2}{*}{B Train 30k?}  & \multirow{2}{*}{N/A}     & A Test Full    &   76.1 \\
\cmidrule{6-7} 
&   &    &   &    & B Test Full?    &   92.7  \\

\midrule				
CNN+GRU+FiLM & \multirow{5}{*}{A Train Full?}   & \multirow{5}{*}{N/A}  & \multirow{2}{*}{--} & \multirow{2}{*}{--}  &   A Valid Full?    &  98.3   \\
\cmidrule{6-7} 
0-Shot &   &    &   &    & B Valid 120k    &   78.8  \\
\cmidrule{4-5}\cmidrule{6-7}
(\cite{perez2017film}) &  &    & \multirow{2}{*}{B Valid 30k}  & \multirow{2}{*}{N/A}     & A Valid Full?    & 81.1  \\
\cmidrule{6-7} 
&   &    &   &    & B Valid 120k    &  96.9  \\

\midrule				
& \multirow{5}{*}{A Train Full?}   & \multirow{5}{*}{N/A}  & \multirow{2}{*}{--} & \multirow{2}{*}{--}  &   A ?    &  98.8   \\
\cmidrule{6-7} 
TbD + reg &   &    &   &    & B ?    &  75.4   \\
\cmidrule{4-5}\cmidrule{6-7}
(\cite{mascharka2018transparency}) &  &    & \multirow{2}{*}{B Valid 30k}  & \multirow{2}{*}{N/A}     & A ?    &  96.9 \\
\cmidrule{6-7} 
&   &    &   &    & B ?   &  96.3  \\

\midrule				
& \multirow{5}{*}{A Train 630k}   & \multirow{5}{*}{97.02}  & \multirow{2}{*}{--} & \multirow{2}{*}{--}  &   A Valid Full    &     96.88 \\
\cmidrule{6-7} 
MAC &   &    &   &    & B Valid Full   &  79.54   \\
\cmidrule{4-5}\cmidrule{6-7}
(our results) &  &    & \multirow{2}{*}{B Valid 30k}  & \multirow{2}{*}{97.91}     & A Valid Full    &  92.06 \\
\cmidrule{6-7} 
&   &    &   &    & B Valid 120k    &   95.62 \\

\midrule				
& \multirow{5}{*}{A Train 630k}   & \multirow{5}{*}{96.09}  & \multirow{2}{*}{--} & \multirow{2}{*}{--}  &   A Valid Full    &     95.91 \\
\cmidrule{6-7} 
S-MAC &   &    &   &    & B Valid Full   &  78.71   \\
\cmidrule{4-5}\cmidrule{6-7}
(our results) &  &    & \multirow{2}{*}{B Valid 30k}  & \multirow{2}{*}{96.85}     & A Valid Full    &  91.24 \\
\cmidrule{6-7} 
&   &    &   &    & B Valid 120k    &   94.55 \\

@@

\cite{perez2017film})

We train our best model architecture on Condition A and report accuracies on Conditions A and B, before and
after fine-tuning on B, in Figure 9. Our results indicate FiLM
surpasses other visual reasoning models at learning general
concepts.

FiLM ValB accuracy reported on ValB without the 30K fine-tuning samples 
Accuracy before and after fine-tuning on 30K of ValB

Training A

@@

Performance comparison against the current state-of-the-
art model on the CoGenT dataset having trained only on Condition
A data (middle column) and after fine-tuning on a small amount
of data with novel attributes (right column).

Like pre-
vious  work  [14],  our  performance  is  worse  on  Condition
B than Condition A after training only using Condition A
data.  As Table 3 shows, our model achieves 98.8\% accu-
racy on Condition A, but only 75.4\% on Condition B. Fol-
lowing Johnson
et al
. [14], we then fine-tune our model us-
ing 3k images and 30k questions from the Condition B data.
Whereas other models see a significant drop in performance
on the Condition A data after fine-tuning, our model main-
tains high performance.  As Table 3 shows, our model can
effectively learn from a small amount of Condition B data.
We achieve 96.9\% accuracy on Condition A and 96.3\% ac-
curacy on Condition B after fine-tuning, far surpassing the
highest-reported 76.1\% Condition A and 92.7\% Condition
B accuracy.
